### 2011-02-24 trunk/deliverables/D4_3/fast_d4_3_2.tex
added a few more comments
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1286 d8b0c59b-6544-0410-94d9-83a5658a058e

\textcolor{red}{WSDL is usually used with SOAP and XML, JSON wouldn't be common in this case. And from my understanding, the user has to hand-write the POST body? therefore the SOAP message? that's doable, but pretty hard and tedious. - Ismael
Well as I understood, in case of WSDL the post body is structured (XML?). Thus, we parse that body, identify the key value pairs of the parameters and come up with an input form as we do for URL parameters. Easily done. 
I have changed the text above slightly to reflect this better.
}

\textcolor{red}{Is PUT and DELETE supported? if so, how? - Ismael
Well, it will be supported for the review meeting. Actually Dennis has done a lot of work on this and it is pretty complete. 
After all a post request looks very much like a get request. Yes, the data is provided in some body. But, the FAST API, that works as relay for us, provides a method, where you pass an url, the request kind (GET, PUT, DELETE, ...) and the parameters. Depending on the kind, this method puts the parameters either in the URL or in some body. No difference for us.
}

>>>>

\textcolor{red}{WSDL is usually used with SOAP and XML, JSON wouldn't be common in this case. And from my understanding, the user has to hand-write the POST body? therefore the SOAP message? that's doable, but pretty hard and tedious. - Ismael
\textcolor{blue}{Well as I understood, in case of WSDL the post body is structured (XML?). Thus, we parse that body, identify the key value pairs of the parameters and come up with an input form as we do for URL parameters. Easily done. 
I have changed the text above slightly to reflect this better. - Albert}
\textcolor{red}{yes and no. it uses SOAP, which relies on XML, but it's something different. the SOAP message will have more info that pre-/post-condition needs. - Ismael}

\textcolor{red}{Is PUT and DELETE supported? if so, how? - Ismael}
\textcolor{blue}{Well, it will be supported for the review meeting. Actually Dennis has done a lot of work on this and it is pretty complete. 
After all a post request looks very much like a get request. Yes, the data is provided in some body. But, the FAST API, that works as relay for us, provides a method, where you pass an url, the request kind (GET, PUT, DELETE, ...) and the parameters. Depending on the kind, this method puts the parameters either in the URL or in some body. No difference for us.}
\textcolor{red}{ok, grand!}
